### 2022-12-21 submission/response_to_reviewers.md

---
geometry: margin=1.0in
fontfamily: helvet
fontsize: 14pt
header-includes:
  - \raggedright
  - \renewcommand{\familydefault}{\sfdefault}
  - \usepackage[T1]{fontenc}
---

**Reviewer #1:**

**This manuscript describes an educational resource - the Riffomonas YouTube channel, developed by the author. I am familiar with the channel and some of its content - in order to make this a more compelling MRA, better descriptions of the resource would be nice. For example, would you be able to provide a table links to specific episodes or modules and what's covered in that module? Would you be able to use this table to also guide readers as to what they could do with that content they learn?**

**Reviewer #2:**

**First, this is an awesome resource, so I'm glad the author is choosing to report it in this venue.**

**Second, there needs to be more information on the specific content. A table is a good idea. There are playlists that could be referenced, but a more detailed description of what someone could hope to gain from going to the site would make this a more valuable resource since this could serve as the entry point for new users. E.g., what kind of code is taught (R, Python, etc.)? What kind of data types are analyzed (16S amplicon, metagenomics, etc.)? What kind of specific skills can be learned (microbiome data analysis, database curation, working with git, multivariate statistics, etc.)?**

I appreciate the enthusiasm that the reviewers both shared for the manuscript that I submitted to describe the *Riffomonas* YouTube channel as an educational resource. I have added a table that lists the various playlists and the number of videos in each that that are available on the channel. I have given the playlists titles that I hope are sufficiently descriptive to indicate they type of topics they contain. The new table includes a section indicating the general topics covered in the videos and a section that lists the types of projects that I developed over the videos. As I will continue to add videos to the channel in 2023 and beyond, I think the broad overview of topics and projects presented in Table 1 serves as an illustrative description of the videos. Because a single video may cover multiple topics the numbers do not add up to the total number of videos.

The submitted version of the manuscript embeds hyperlinks in each of the titles of the playlists. I realize that this format may not work for a printed PDF, but am optimistic that it would be possible to retain the hyperlinked titles for the online HTML and PDF versions. Unfortunately, the playlist hyperlinks are really not well formatted for printing. For example, the videos in the "Data visualization with R's tidyverse and allied packages" playlist can be found at https://youtube.com/playlist?list=PLmNrK_nkqBpKHYucwmN6YlNjoyeWoGBYu
